Pyro-Velocity

### 2024-03-25 nbs/tutorials/introduction_v013.qmd
refactor(nbs): retain 013 and 020 introductions Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>

[Pyro-Velocity](https://docs.pyrovelocity.net) is a library for probabilistic inference in minimal models approximating gene expression dynamics from, possibly multimodal, single-cell sequencing data.
It provides posterior estimates of gene expression parameters, predictive estimates of gene expression states, and local estimates of cell state transition probabilities.
It can be used as a component in frameworks that attempt to retain the ability to propagate uncertainty in predicting: distributions over cell fates from subpopulations of cell states, response to cell state perturbations, or candidate genes or gene modules that correlate with determination of specific cell fates.

@@

We currently support installation and usage in a linux 64-bit development environment with access to a GPU.
An [IaC](https://en.wikipedia.org/wiki/Infrastructure_as_code) setup that works with [GCP](https://registry.terraform.io/providers/hashicorp/google/latest/docs) is documented in [reproducibility/environment/README.md](reproducibility/environment/README.md).
Before proceeding to setup a minimal development environment, please fork this repository and clone a copy of your fork to your development machine. Unless otherwise mentioned, all commands assume your current working directory is the root of your local copy of your fork of this repository.

@@

Also see [contributing](./docs/contributing.md).

>>>>

`Pyro-Velocity` is a Bayesian, generative, and multivariate RNA velocity model to estimate uncertainty in predictions of future cell states from minimal models approximating splicing dynamics. This approach models raw sequencing counts with synchronized cell time across all expressed genes to provide quantifiable information on cell fate choice and developmental trajectory dynamics.

@@

We currently support installation and usage in a linux 64-bit development environment with access to a GPU.
An [IaC](https://en.wikipedia.org/wiki/Infrastructure_as_code) setup that works with [GCP](https://registry.terraform.io/providers/hashicorp/google/latest/docs) is documented in [reproducibility/environment/README.md](https://github.com/pinellolab/pyrovelocity/blob/main/reproducibility/environment/README.md).
Before proceeding to setup a minimal development environment, please fork this repository and clone a copy of your fork to your development machine. Unless otherwise mentioned, all commands assume your current working directory is the root of your local copy of your fork of this repository.

@@

Also see [contributing](https://github.com/pinellolab/pyrovelocity/blob/main/docs/contributing.md).
